### 2020-05-02 thesis_template/3_Body/model/knn.tex
proceded discussion

Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
frequency of memory deallocations. Parameter k specifies dimension of feature matrices. This determines size of intermediate data structures and numeric matrices.

@@

\subsection{Result}
\label{sec:history}

@@

>>>>

Number of batch controls number and size of batch for each partition. This parameter varies size of intermediate data structures and numeric matrices, and 
frequency of memory deallocations. 
The parameter k specifies number of dimension of feature matrices created out of preprocess phase. 
By controlling this, it determines size of intermediate data structures and numeric matrices.

@@

\subsection{Result}
\label{sec:history}
Figure~\ref{fig:total}, ~\ref{fig:preprocess}, and ~\ref{fig:query} show the runtime performance of our KNN algorithms in total, preprocess, and query phase respectively. 
The algorithms used in our experiments are indexed in Table~\ref{tab:algorithm}. We call each algorithm in algorithm number for easy understanding.
The Algorithm 3 with 20K and 25K dimension, and the Algorithm 1 with 25K dimension whose runtime is showing 0 seconds are algorithms that are terminated during execution due to fail of memory allocation.

Figure~\ref{fig:total} shows Algorithm 8 shows much slower performance compare to the other algorithms.
Algorithm 7 also starts to slow down as we increase the number of dimension.

As shown in Figure~\ref{fig:preprocess}, the algorithms using Arc is much slower than using deep-copy in preprocessing phase. 
Algorithm 6 is 38\%  slower than Algorithm 6 in dimension of 25K. 
In addition, the algorithms with strategy 2 are slower than with strategy 1. 
For example, Algorithm 6 is about 85\% slower than one Algorithm 2 in dimension of 25K.
The algorithms with 3 batches are slower that ones with 2 batches. Furthermore, as we increase the number of dimension, the number of batch becomes more and more critical to runtime performance of the algorithms with deep-copy.
The runtime ratios of difference from Algorithm 7 to Algorithm 8 are about 44\%, 28\%, and 39\% for dimension of 15K, 20K, and 25K respectively. 
However, those from Algorithm 5 to Algorithm 6 are about 11\%, 28\%, and 54\%. The ratios of difference increase proportionally to the number of dimension.

In query phase, Algorithm 8 is much slower than the others in different parameter settings.
Algorithm 7 starts to slow down as number of dimension is increased.

\begin{table}
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|l|l|l|l|}
    \hline
    Algorithm number & Method    & Strategy & Number of batch \\ \hline
    1                & deep-copy & 1        & 2               \\ \hline
    2                & deep-copy & 1        & 3               \\ \hline
    3                & arc       & 1        & 2               \\ \hline
    4                & arc       & 1        & 3               \\ \hline
    5                & deep-copy & 2        & 2               \\ \hline
    6                & deep-copy & 2        & 3               \\ \hline
    7                & arc       & 2        & 2               \\ \hline
    8                & arc       & 2        & 3               \\ \hline
    \end{tabular}
    \caption{Index of Algorithm}
    \label{tab:algorithm}
 \end{table}

@@

\subsection{Discussion}
\label{sec:history}
In preprocess phase, the algorithms using Arc method performs worse that one with deep-copy method. 
This result may seem to contradict to the result of Experiment 4 in Section~\ref{sec:eval_treeagg}.
In Experiment 4, complex objects, CustomerOwned, are cloned with Arc or deep-copied. 
In this Experiment 5, we however get Arc or deep-copy of String instead of complex object.
The result explains deep-copying String is much inexpensive than deep-copying the complex object and 
actually efficient than using Arc to share String. 
Therefore, we need to make decision which method to use depending on size and complexity of objects.

In addition, use of different strategies in preprocess phase explains how deallocations of intermediate data structures and drops of their variables impact algorithm's runtime performance.
The result shows deallocations of intermediate data costs a lot; Algorithm 6 is 85\% slower than Algorithm 2.
This may be more severe bottleneck for algorithms using Arc; Algorithm 8 is 102\% slower than Algorithm 4.
This is the same reason explained in Experiment 4. 
Arc has to check reference count and its atomic operation is expensive.

The impact of number of batch can explain how frequency of memory de/allocation affects runtime performance. 
Dealing with more number of batch has negative impacts to runtime performance, because it triggers more frequent memory de/allocation.
In addition, as we increase the number of dimension, the ration of runtime difference among different numbers of batch for the algorithms with deep-copy, but not for ones with Arc.
This is because algorithm with Arc does not de/allocate memory as much frequent as ones with deep-copy.
The intermediate datas mealy get reference to String values without actually allocating memory for copied Strings.
